InteroceptionScale (study 2) - Data Analysis

### 2025-07-01 study2/analysis/2_analysis.qmd
update

```{r}
#| code-fold: false

items <- select(df, starts_with("MINT_"))
names(items) <- str_remove(names(items), "MINT_")
```

@@

cleanlabels <- function(x, qname=FALSE) {
  is_factor <- FALSE
  if(is.factor(x)) {
    is_factor <- TRUE
    vec <- x
    x <- levels(x)
  }

@@

@@

@@

@@

```{r}
table_models <- function(models) {
  test <- test_performance(models)
  table <- compare_performance(models, metrics=c("R2", "BIC"))
  test$Model <- NULL
  test$Omega2 <- NULL
  test$p_Omega2 <- NULL
  test$R2 <- table$R2
  test$BIC <- table$BIC

@@

  if(length(coefs) == length(models)) test$Coefficient <- coefs
  format(test, zap_small = TRUE)
}

# Individual predictors ------------------------------------------------------

@@

```{r}
preds_dif <- compare_predictors("TAS_DIF")
display(preds_dif$table, title="DIF")
preds_dif$p
mods_dif <- compare_models_lm("TAS_DIF")
display(mods_dif, title="DIF")

preds_ddf <- compare_predictors("TAS_DDF")
display(preds_ddf$table, title="DDF")
preds_ddf$p
mods_ddf <- compare_models_lm("TAS_DDF")
display(mods_ddf, title="DDF")

preds_eot <- compare_predictors("TAS_EOT")
display(preds_eot$table, title="EOT")
preds_eot$p
mods_eot <- compare_models_lm("TAS_EOT")
display(mods_eot, title="EOT")
```

@@

```{r}
preds_ls <- compare_predictors("LifeSatisfaction")
display(preds_ls$table, title="Life Satisfaction")
preds_ls$p
mods_ls <- compare_models_lm("LifeSatisfaction")
display(mods_ls, title="Life Satisfaction")

preds_anx <- compare_predictors("PHQ4_Anxiety")
display(preds_anx$table, title="PHQ4 Anxiety")
preds_anx$p
mods_anx <- compare_models_lm("PHQ4_Anxiety")
display(mods_anx, title="PHQ4 Anxiety")

preds_dep <- compare_predictors("PHQ4_Depression")
display(preds_dep$table, title="PHQ4 Depression")
preds_dep$p
mods_dep <- compare_models_lm("PHQ4_Depression")
display(mods_dep, title="PHQ4 Depression")
```

@@

```{r}
preds_arou <- compare_predictors("ERS_Arousal")
display(preds_arou$table, title="ERS Arousal")
preds_arou$p
mods_arou <- compare_models_lm("ERS_Arousal")
display(mods_arou, title="ERS Arousal")

preds_sens <- compare_predictors("ERS_Sensitivity")
display(preds_sens$table, title="ERS Sensitivity")
preds_sens$p
mods_sens <- compare_models_lm("ERS_Sensitivity")
display(mods_sens, title="ERS Sensitivity")

preds_pers <- compare_predictors("ERS_Persistence")
display(preds_pers$table, title="ERS Persistence")
preds_pers$p
mods_pers <- compare_models_lm("ERS_Persistence")
display(mods_pers, title="ERS Persistence")
```

@@

```{r}
make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
         select(df, starts_with("CEFSA")))

make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
         select(df, starts_with("CEFSA")))
```

```{r}
preds_cefsabody <- compare_predictors("CEFSA_Body")
display(preds_cefsabody$table, title="CEFSA - Body")
preds_cefsabody$p
mods_cefsabody <- compare_models_lm("CEFSA_Body")
display(mods_cefsabody, title="CEFSA - Body")

preds_cefsaself <- compare_predictors("CEFSA_Self")
display(preds_cefsaself$table, title="CEFSA - Self")
preds_cefsaself$p
mods_cefsaself <- compare_models_lm("CEFSA_Self")
display(mods_cefsaself, title="CEFSA - Self")

preds_cefsaemo <- compare_predictors("CEFSA_Emotion")
display(preds_cefsaemo$table, title="CEFSA - Emotion")
preds_cefsaemo$p
mods_cefsaemo <- compare_models_lm("CEFSA_Emotion")
display(mods_cefsaemo, title="CEFSA - Emotion")

preds_cefsareal <- compare_predictors("CEFSA_Reality")
display(preds_cefsareal$table, title="CEFSA - Reality")
preds_cefsareal$p
mods_cefsareal <- compare_models_lm("CEFSA_Reality")
display(mods_cefsareal, title="CEFSA - Reality")

preds_cefsacon <- compare_predictors("CEFSA_Connection")
display(preds_cefsacon$table, title="CEFSA - Connection")
preds_cefsacon$p
mods_cefsacon <- compare_models_lm("CEFSA_Connection")
display(mods_cefsacon, title="CEFSA - Connection")

preds_cefsagency <- compare_predictors("CEFSA_Agency")
display(preds_cefsagency$table, title="CEFSA - Agency")
preds_cefsagency$p
mods_cefsagency <- compare_models_lm("CEFSA_Agency")
display(mods_cefsagency, title="CEFSA - Agency")
```

@@

```{r}
make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
         select(df, starts_with("CERQ")))

make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
         select(df, starts_with("CERQ")))
```

```{r}
preds_cerqreapp <- compare_predictors("CERQ_PositiveReappraisal")
display(preds_cerqreapp$table, title="CERQ - Positive Reappraisal")
preds_cerqreapp$p
mods_cerqreapp <- compare_models_lm("CERQ_PositiveReappraisal")
display(mods_cerqreapp, title="CERQ - Positive Reappraisal")

preds_cerqrefocus <- compare_predictors("CERQ_PositiveRefocusing")
display(preds_cerqrefocus$table, title="CERQ - Positive Refocusing")
preds_cerqrefocus$p
mods_cerqrefocus <- compare_models_lm("CERQ_PositiveRefocusing")
display(mods_cerqrefocus, title="CERQ - Positive Refocusing")

preds_cerqpersp <- compare_predictors("CERQ_Perspective")
display(preds_cerqpersp$table, title="CERQ - Perspective")
preds_cerqpersp$p
mods_cerqpersp <- compare_models_lm("CERQ_Perspective")
display(mods_cerqpersp, title="CERQ - Perspective")

preds_cerqacceptance <- compare_predictors("CERQ_Acceptance")
display(preds_cerqacceptance$table, title="CERQ - Acceptance")
preds_cerqacceptance$p
mods_cerqacceptance <- compare_models_lm("CERQ_Acceptance")
display(mods_cerqacceptance, title="CERQ - Acceptance")
```

@@

```{r}
make_cor(select(df, starts_with("MINT"), -matches("[[:digit:]]")), 
         select(df, starts_with("PI")))

make_cor(select(df, starts_with("MAIA"), IAS, BPQ), 
         select(df, starts_with("PI")))
```

```{r}
preds_pialive <- compare_predictors("PI_Alive")
display(preds_pialive$table, title="Primals - Alive")
preds_pialive$p
mods_pialive <- compare_models_lm("PI_Alive")
display(mods_pialive, title="Primals - Alive")

preds_pisafe <- compare_predictors("PI_Safe")
display(preds_pisafe$table, title="Primals - Safe")
preds_pisafe$p
mods_pisafe <- compare_models_lm("PI_Safe")
display(mods_pisafe, title="Primals - Safe")

preds_pient <- compare_predictors("PI_Enticing")
display(preds_pient$table, title="Primals - Enticing")
preds_pient$p
mods_pient <- compare_models_lm("PI_Enticing")
display(mods_pient, title="Primals - Enticing")

preds_pigood <- compare_predictors("PI_Good")
display(preds_pigood$table, title="Primals - Good")
preds_pigood$p
mods_pigood <- compare_models_lm("PI_Good")
display(mods_pigood, title="Primals - Good")
```

@@

```{r}
preds_mood <- compare_predictors("Disorders_Psychiatric_Mood")
display(preds_mood$table, title="Mood Disorders")
preds_mood$p
mods_mood <- compare_models_glm("Disorders_Psychiatric_Mood")
display(mods_mood$table, title="Mood Disorders")
mods_mood$p
```

```{r}
preds_moodt <- compare_predictors("Disorders_Psychiatric_MoodTreatment")
display(preds_moodt$table, title="Mood Disorders (with Treatment)")
preds_moodt$p
mods_moodt <- compare_models_glm("Disorders_Psychiatric_MoodTreatment",
                                 title="Mood Disorders", subtitle = "MDD, GAD, Bipolar (with Treatment)")
display(mods_moodt$table, title="Mood Disorders (with Treatment)")
mods_moodt$p
```

@@

```{r}
preds_anxdis <- compare_predictors("Disorders_Psychiatric_Anxiety")
display(preds_anxdis$table, title="Anxiety Disorders")
preds_anxdis$p
mods_anxdis <- compare_models_glm("Disorders_Psychiatric_Anxiety")
display(mods_anxdis$table, title="Anxiety Disorders")
mods_anxdis$p
```

```{r}
preds_anxdist <- compare_predictors("Disorders_Psychiatric_AnxietyTreatment")
display(preds_anxdist$table, title="Anxiety Disorders (with Treatment)")
preds_anxdist$p
mods_anxdist <- compare_models_glm("Disorders_Psychiatric_AnxietyTreatment")
display(mods_anxdist$table, title="Anxiety Disorders (with Treatment)")
mods_anxdist$p
```

@@

```{r}
preds_eat <- compare_predictors("Disorders_Psychiatric_Eating")
display(preds_eat$table, title="Eating Disorders")
preds_eat$p
mods_eat <- compare_models_glm("Disorders_Psychiatric_Eating")
display(mods_eat$table, title="Eating Disorders")
mods_eat$p
```

@@

```{r}
preds_addict <- compare_predictors("Disorders_Psychiatric_Addiction")
display(preds_addict$table, title="Addiction")
preds_addict$p
mods_addict <- compare_models_glm("Disorders_Psychiatric_Addiction")
display(mods_addict$table, title="Addiction")
mods_addict$p
```

@@

```{r}
preds_adhd <- compare_predictors("Disorders_Psychiatric_ADHD")
display(preds_adhd$table, title="ADHD")
preds_adhd$p
mods_adhd <- compare_models_glm("Disorders_Psychiatric_ADHD",
                                title = "ADHD", subtitle = "Attention Deficit/Hyperactivity Disorder")
display(mods_adhd$table, title="ADHD")
mods_adhd$p
```

@@

```{r}
preds_asd <- compare_predictors("Disorders_Psychiatric_Autism")
display(preds_asd$table, title="Autism")
preds_asd$p
mods_asd <- compare_models_glm("Disorders_Psychiatric_Autism",
                                title = "ASD", subtitle = "Autism Spectrum Disorder")
display(mods_asd$table, title="Autism")
mods_asd$p
```

@@

```{r}
preds_bpd <- compare_predictors("Disorders_Psychiatric_Borderline")
display(preds_bpd$table, title="Borderline Personality Disorder")
preds_bpd$p
mods_bpd <- compare_models_glm("Disorders_Psychiatric_Borderline")
display(mods_bpd$table, title="Borderline Personality Disorder")
mods_bpd$p
```

@@

```{r}
preds_afferent <- compare_predictors("Disorders_Somatic_AfferentSensitivity")
display(preds_afferent$table, title="Afferent Sensitivity Symptoms")
preds_afferent$p
mods_afferent <- compare_models_glm("Disorders_Somatic_AfferentSensitivity",
                                    title="Afferent Sensitivity Symptoms",
                                    subtitle = "Migraine, neuropathy, muscle tension, dizziness, ...")
display(mods_afferent$table, title="Afferent Sensitivity Symptoms")
mods_afferent$p
```

@@

```{r}
preds_central <- compare_predictors("Disorders_Somatic_CentralSensitization")
display(preds_central$table, title="Central Sensitization Symptoms")
preds_central$p
mods_central <- compare_models_glm("Disorders_Somatic_CentralSensitization",
                                   title="Central Sensitization Symptoms",
                                   subtitle = "Fibromyalgia, chronic fatigue, back pain, IBS, ...")
display(mods_central$table, title="Central Sensitization Symptoms")
mods_central$p
```

@@

```{r}
preds_autonomic <- compare_predictors("Disorders_Somatic_AutonomicDysfunction")
display(preds_autonomic$table, title="Autonomic Dysfunction")
preds_autonomic$p
mods_autonomic <- compare_models_glm("Disorders_Somatic_AutonomicDysfunction",
                                     title="Autonomic Dysfunction",
                                     subtitle = "Hypermobility, chest pain, hypo/hypertension, ....")
display(mods_autonomic$table, title="Autonomic Dysfunction")
mods_autonomic$p
```

@@

```{r}
preds_immune <- compare_predictors("Disorders_Somatic_ImmuneInflammatory")
display(preds_immune$table, title="Immune-Inflammatory Symptoms")
preds_immune$p
mods_immune <- compare_models_glm("Disorders_Somatic_ImmuneInflammatory",
                                  title="Immune-Inflammatory Symptoms",
                                  subtitle = "Allergies, asthma, eczema, autoimmune, ...")
display(mods_immune$table, title="Immune-Inflammatory Symptoms")
mods_immune$p
```

@@

```{r}
preds_age <- compare_predictors("Age")
display(preds_age$table, title="Age")
preds_age$p
mods_age <- compare_models_lm("Age")
display(mods_age, title="Age")
```

@@

preds_sex <- compare_predictors("Sex")
display(preds_sex$table, title="Sex")
preds_sex$p
mods_sex <- compare_models_glm("Sex")
display(mods_sex$table, title="Sex")
mods_sex$p
```

@@

```{r}
preds_bmi <- compare_predictors("BMI")
display(preds_bmi$table, title="BMI")
preds_bmi$p
mods_bmi <- compare_models_lm("BMI")
display(mods_bmi, title="BMI")
```

@@

```{r}
preds_physactiv <- compare_predictors("Physical_Active")
display(preds_physactiv$table, title="Physical Activity")
preds_physactiv$p
mods_physactiv <- compare_models_lm("Physical_Active")
display(mods_physactiv, title="Physical Activity")
```

@@

```{r}
preds_wearN <- compare_predictors("Wearables_Number", family = "poisson")
display(preds_wearN$table, title="Wearables Number")
preds_wearN$p
```

@@

```{r}
df$Wearables_HeartOwn <- ifelse(df$Wearables_Heart == "Not owning", 0, 1) 
preds_wearHeartOwn <- compare_predictors("Wearables_HeartOwn")
display(preds_wearHeartOwn$table, title="Wearables Heart Ownership")
preds_wearHeartOwn$p
mods_wearHeartOwn <- compare_models_glm("Wearables_HeartOwn")
display(mods_wearHeartOwn$table, title="Wearables Heart Ownership")
mods_wearHeartOwn$p

preds_wearHeartImp <- compare_predictors("Wearables_HeartImportance")
display(preds_wearHeartImp$table, title="Wearables Heart Importance")
preds_wearHeartImp$p
mods_wearHeartImp <- compare_models_lm("Wearables_HeartImportance")
display(mods_wearHeartImp, title="Wearables Heart Importance")
```

@@

```{r}
df$Wearables_SleepOwn <- ifelse(df$Wearables_Sleep == "Not owning", 0, 1)
preds_wearSleepOwn <- compare_predictors("Wearables_SleepOwn")
display(preds_wearSleepOwn$table, title="Wearables Sleep Ownership")
preds_wearSleepOwn$p
mods_wearSleepOwn <- compare_models_glm("Wearables_SleepOwn")
display(mods_wearSleepOwn$table, title="Wearables Sleep Ownership")

preds_wearSleepImp <- compare_predictors("Wearables_SleepImportance")
display(preds_wearSleepImp$table, title="Wearables Sleep Importance")
preds_wearSleepImp$p
mods_wearSleepImp <- compare_models_lm("Wearables_SleepImportance")
display(mods_wearSleepImp, title="Wearables Sleep Importance")
```

>>>>

```{r}
items <- select(df, starts_with("MINT_"))
names(items) <- str_remove(names(items), "MINT_")
```

See the list of item labels in the code below.

@@

```

```{r}
cleanlabels <- function(x, qname=FALSE) {
  is_factor <- FALSE
  if(is.factor(x)) {
    is_factor <- TRUE
    vec <- x
    x <- levels(x)
  }

@@

Additionally to EGA, we explored Hierarchical Clustering to see if the results are consistent.

@@

To help us in confirming which clusters to keep or to remove, we empirically tested the "importance" (normalized R2) of each cluster in predicting various outcomes present in our dataset, and aggregating the average importance of each cluster different categories of outcomes. 
This approach yielded patterns which highlighted some clusters as providing a unique contribution (e.g., Olfa and Sati).

@@

Initially, we fought about also removing Olfa and Sati to provide a more parsimonious and balanced final set, but they seem to withhold interesting value.

@@

```{r}
table_models <- function(models) {
  test <- test_performance(models)
  table <- compare_performance(models, metrics=c("R2", "BIC"))
  test$Model <- NULL
  test$Omega2 <- NULL
  test$p_Omega2 <- NULL
  test$LR <- NULL
  test$p_LR <- NULL
  test$R2 <- table$R2
  test$BIC <- table$BIC

@@

  test <- datawizard::data_select(test, c("Name", "R2", "BIC", "BF"))

  if(length(coefs) == length(models)) test$Coefficient <- coefs

  test
}

display_models <- function(table, title = "", subtitle = "") {
  numcols <- c("R2", "BIC", "Coefficient")[c("R2", "BIC", "Coefficient") %in% names(table)]
  table |> 
    mutate(BF = format_bf(BF, name = NULL, stars = TRUE)) |> 
    gt::gt() |> 
    gt::fmt_number(columns = numcols, decimals = 3) |>
    gt::tab_header(title = title, subtitle = subtitle) |>
    gt::data_color(
      columns = c("R2"),
      palette = c("white", "green")
    ) |> 
    gt::data_color(
      columns = c("BIC"),
      palette = c("green", "white")
    ) |> 
    gt::opt_interactive(use_compact_mode=TRUE)

}
# Individual predictors ------------------------------------------------------

@@

```{r}
preds_dif <- compare_predictors("TAS_DIF")
display_models(preds_dif$table, title="Best Predictor", subtitle = "TAS - DIF")
preds_dif$p
mods_dif <- compare_models_lm("TAS_DIF")
display_models(mods_dif, title="Best Model", subtitle = "DIF")

preds_ddf <- compare_predictors("TAS_DDF")
display_models(preds_ddf$table, title="Best Predictor", subtitle = "DDF")
preds_ddf$p
mods_ddf <- compare_models_lm("TAS_DDF")
display_models(mods_ddf, title="Best Model", subtitle = "DDF")

preds_eot <- compare_predictors("TAS_EOT")
display_models(preds_eot$table, title="Best Predictor", subtitle = "EOT")
preds_eot$p
mods_eot <- compare_models_lm("TAS_EOT")
display_models(mods_eot, title="Best Model", subtitle = "EOT")
```

@@

```{r}
preds_ls <- compare_predictors("LifeSatisfaction")
display_models(preds_ls$table, title="Best Predictor", subtitle = "Life Satisfaction")
preds_ls$p
mods_ls <- compare_models_lm("LifeSatisfaction")
display_models(mods_ls, title="Best Model", subtitle = "Life Satisfaction")

preds_anx <- compare_predictors("PHQ4_Anxiety")
display_models(preds_anx$table, title="Best Predictor", subtitle = "PHQ4 Anxiety")
preds_anx$p
mods_anx <- compare_models_lm("PHQ4_Anxiety")
display_models(mods_anx, title="Best Model", subtitle = "PHQ4 Anxiety")

preds_dep <- compare_predictors("PHQ4_Depression")
display_models(preds_dep$table, title="Best Predictor", subtitle = "PHQ4 Depression")
preds_dep$p
mods_dep <- compare_models_lm("PHQ4_Depression")
display_models(mods_dep, title="Best Model", subtitle = "PHQ4 Depression")
```

@@

```{r}
preds_arou <- compare_predictors("ERS_Arousal")
display_models(preds_arou$table, title="Best Predictor", subtitle = "ERS Arousal")
preds_arou$p
mods_arou <- compare_models_lm("ERS_Arousal")
display_models(mods_arou, title="Best Model", subtitle = "ERS Arousal")

preds_sens <- compare_predictors("ERS_Sensitivity")
display_models(preds_sens$table, title="Best Predictor", subtitle = "ERS Sensitivity")
preds_sens$p
mods_sens <- compare_models_lm("ERS_Sensitivity")
display_models(mods_sens, title="Best Model", subtitle = "ERS Sensitivity")

preds_pers <- compare_predictors("ERS_Persistence")
display_models(preds_pers$table, title="Best Predictor", subtitle = "ERS Persistence")
preds_pers$p
mods_pers <- compare_models_lm("ERS_Persistence")
display_models(mods_pers, title="Best Model", subtitle = "ERS Persistence")
```

@@

make_cor(select(df, starts_with("CEFSA")),
         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
```

```{r}
preds_cefsabody <- compare_predictors("CEFSA_Body")
display_models(preds_cefsabody$table, title="Best Predictor", subtitle = "CEFSA - Body")
preds_cefsabody$p
mods_cefsabody <- compare_models_lm("CEFSA_Body")
display_models(mods_cefsabody, title="Best Model", subtitle = "CEFSA - Body")

preds_cefsaself <- compare_predictors("CEFSA_Self")
display_models(preds_cefsaself$table, title="Best Predictor", subtitle = "CEFSA - Self")
preds_cefsaself$p
mods_cefsaself <- compare_models_lm("CEFSA_Self")
display_models(mods_cefsaself, title="Best Model", subtitle = "CEFSA - Self")

preds_cefsaemo <- compare_predictors("CEFSA_Emotion")
display_models(preds_cefsaemo$table, title="Best Predictor", subtitle = "CEFSA - Emotion")
preds_cefsaemo$p
mods_cefsaemo <- compare_models_lm("CEFSA_Emotion")
display_models(mods_cefsaemo, title="Best Model", subtitle = "CEFSA - Emotion")

preds_cefsareal <- compare_predictors("CEFSA_Reality")
display_models(preds_cefsareal$table, title="Best Predictor", subtitle = "CEFSA - Reality")
preds_cefsareal$p
mods_cefsareal <- compare_models_lm("CEFSA_Reality")
display_models(mods_cefsareal, title="Best Model", subtitle = "CEFSA - Reality")

preds_cefsacon <- compare_predictors("CEFSA_Connection")
display_models(preds_cefsacon$table, title="Best Predictor", subtitle = "CEFSA - Connection")
preds_cefsacon$p
mods_cefsacon <- compare_models_lm("CEFSA_Connection")
display_models(mods_cefsacon, title="Best Model", subtitle = "CEFSA - Connection")

preds_cefsagency <- compare_predictors("CEFSA_Agency")
display_models(preds_cefsagency$table, title="Best Predictor", subtitle = "CEFSA - Agency")
preds_cefsagency$p
mods_cefsagency <- compare_models_lm("CEFSA_Agency")
display_models(mods_cefsagency, title="Best Model", subtitle = "CEFSA - Agency")
```

@@

make_cor(select(df, starts_with("CERQ")),
         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
```

```{r}
preds_cerqreapp <- compare_predictors("CERQ_PositiveReappraisal")
display_models(preds_cerqreapp$table, title="Best Predictor", subtitle = "CERQ - Positive Reappraisal")
preds_cerqreapp$p
mods_cerqreapp <- compare_models_lm("CERQ_PositiveReappraisal")
display_models(mods_cerqreapp, title="Best Model", subtitle = "CERQ - Positive Reappraisal")

preds_cerqrefocus <- compare_predictors("CERQ_PositiveRefocusing")
display_models(preds_cerqrefocus$table, title="Best Predictor", subtitle = "CERQ - Positive Refocusing")
preds_cerqrefocus$p
mods_cerqrefocus <- compare_models_lm("CERQ_PositiveRefocusing")
display_models(mods_cerqrefocus, title="Best Model", subtitle = "CERQ - Positive Refocusing")

preds_cerqpersp <- compare_predictors("CERQ_Perspective")
display_models(preds_cerqpersp$table, title="Best Predictor", subtitle = "CERQ - Perspective")
preds_cerqpersp$p
mods_cerqpersp <- compare_models_lm("CERQ_Perspective")
display_models(mods_cerqpersp, title="Best Model", subtitle = "CERQ - Perspective")

preds_cerqacceptance <- compare_predictors("CERQ_Acceptance")
display_models(preds_cerqacceptance$table, title="Best Predictor", subtitle = "CERQ - Acceptance")
preds_cerqacceptance$p
mods_cerqacceptance <- compare_models_lm("CERQ_Acceptance")
display_models(mods_cerqacceptance, title="Best Model", subtitle = "CERQ - Acceptance")
```

@@

make_cor(select(df, starts_with("PI")),
         cbind(mint, metamint, select(df, starts_with("MAIA"), IAS, BPQ)))
```

```{r}
preds_pialive <- compare_predictors("PI_Alive")
display_models(preds_pialive$table, title="Best Predictor", subtitle = "Primals - Alive")
preds_pialive$p
mods_pialive <- compare_models_lm("PI_Alive")
display_models(mods_pialive, title="Best Model", subtitle = "Primals - Alive")

preds_pisafe <- compare_predictors("PI_Safe")
display_models(preds_pisafe$table, title="Best Predictor", subtitle = "Primals - Safe")
preds_pisafe$p
mods_pisafe <- compare_models_lm("PI_Safe")
display_models(mods_pisafe, title="Best Model", subtitle = "Primals - Safe")

preds_pient <- compare_predictors("PI_Enticing")
display_models(preds_pient$table, title="Best Predictor", subtitle = "Primals - Enticing")
preds_pient$p
mods_pient <- compare_models_lm("PI_Enticing")
display_models(mods_pient, title="Best Model", subtitle = "Primals - Enticing")

preds_pigood <- compare_predictors("PI_Good")
display_models(preds_pigood$table, title="Best Predictor", subtitle = "Primals - Good")
preds_pigood$p
mods_pigood <- compare_models_lm("PI_Good")
display_models(mods_pigood, title="Best Model", subtitle = "Primals - Good")
```

@@

```{r}
preds_mood <- compare_predictors("Disorders_Psychiatric_Mood")
display_models(preds_mood$table, title="Best Predictor", subtitle = "Mood Disorders")
preds_mood$p
mods_mood <- compare_models_glm("Disorders_Psychiatric_Mood")
display_models(mods_mood$table, title="Best Predictor", subtitle = "Mood Disorders")
mods_mood$p
```

```{r}
preds_moodt <- compare_predictors("Disorders_Psychiatric_MoodTreatment")
display_models(preds_moodt$table, title="Best Predictor", subtitle = "Mood Disorders (with Treatment)")
preds_moodt$p
mods_moodt <- compare_models_glm("Disorders_Psychiatric_MoodTreatment",
                                 title="Mood Disorders", subtitle = "MDD, GAD, Bipolar (with Treatment)")
display_models(mods_moodt$table, title="Best Predictor", subtitle = "Mood Disorders (with Treatment)")
mods_moodt$p
```

@@

```{r}
preds_anxdis <- compare_predictors("Disorders_Psychiatric_Anxiety")
display_models(preds_anxdis$table, title="Best Predictor", subtitle = "Anxiety Disorders")
preds_anxdis$p
mods_anxdis <- compare_models_glm("Disorders_Psychiatric_Anxiety")
display_models(mods_anxdis$table, title="Best Model", subtitle = "Anxiety Disorders")
mods_anxdis$p
```

```{r}
preds_anxdist <- compare_predictors("Disorders_Psychiatric_AnxietyTreatment")
display_models(preds_anxdist$table, title="Best Predictor", subtitle = "Anxiety Disorders (with Treatment)")
preds_anxdist$p
mods_anxdist <- compare_models_glm("Disorders_Psychiatric_AnxietyTreatment")
display_models(mods_anxdist$table, title="Best Model", subtitle = "Anxiety Disorders (with Treatment)")
mods_anxdist$p
```

@@

```{r}
preds_eat <- compare_predictors("Disorders_Psychiatric_Eating")
display_models(preds_eat$table, title="Best Predictor", subtitle = "Eating Disorders")
preds_eat$p
mods_eat <- compare_models_glm("Disorders_Psychiatric_Eating")
display_models(mods_eat$table, title="Best Model", subtitle = "Eating Disorders")
mods_eat$p
```

@@

```{r}
preds_addict <- compare_predictors("Disorders_Psychiatric_Addiction")
display_models(preds_addict$table, title="Best Predictor", subtitle = "Addiction")
preds_addict$p
mods_addict <- compare_models_glm("Disorders_Psychiatric_Addiction")
display_models(mods_addict$table, title="Best Model", subtitle = "Addiction")
mods_addict$p
```

@@

```{r}
preds_adhd <- compare_predictors("Disorders_Psychiatric_ADHD")
display_models(preds_adhd$table, title="Best Predictor", subtitle = "ADHD")
preds_adhd$p
mods_adhd <- compare_models_glm("Disorders_Psychiatric_ADHD",
                                title = "ADHD", subtitle = "Attention Deficit/Hyperactivity Disorder")
display_models(mods_adhd$table, title="Best Model", subtitle = "ADHD")
mods_adhd$p
```

@@

```{r}
preds_asd <- compare_predictors("Disorders_Psychiatric_Autism")
display_models(preds_asd$table, title="Best Predictor", subtitle = "Autism")
preds_asd$p
mods_asd <- compare_models_glm("Disorders_Psychiatric_Autism",
                                title = "ASD", subtitle = "Autism Spectrum Disorder")
display_models(mods_asd$table, title="Best Model", subtitle = "Autism")
mods_asd$p
```

@@

```{r}
preds_bpd <- compare_predictors("Disorders_Psychiatric_Borderline")
display_models(preds_bpd$table, title="Best Predictor", subtitle = "Borderline Personality Disorder")
preds_bpd$p
mods_bpd <- compare_models_glm("Disorders_Psychiatric_Borderline")
display_models(mods_bpd$table, title="Best Model", subtitle = "Borderline Personality Disorder")
mods_bpd$p
```

@@

```{r}
preds_afferent <- compare_predictors("Disorders_Somatic_AfferentSensitivity")
display_models(preds_afferent$table, title="Best Predictor", subtitle = "Afferent Sensitivity Symptoms")
preds_afferent$p
mods_afferent <- compare_models_glm("Disorders_Somatic_AfferentSensitivity",
                                    title="Afferent Sensitivity Symptoms",
                                    subtitle = "Migraine, neuropathy, muscle tension, dizziness, ...")
display_models(mods_afferent$table, title="Best Model", subtitle = "Afferent Sensitivity Symptoms")
mods_afferent$p
```

@@

```{r}
preds_central <- compare_predictors("Disorders_Somatic_CentralSensitization")
display_models(preds_central$table, title="Best Predictor", subtitle = "Central Sensitization Symptoms")
preds_central$p
mods_central <- compare_models_glm("Disorders_Somatic_CentralSensitization",
                                   title="Central Sensitization Symptoms",
                                   subtitle = "Fibromyalgia, chronic fatigue, back pain, IBS, ...")
display_models(mods_central$table, title="Best Model", subtitle = "Central Sensitization Symptoms")
mods_central$p
```

@@

```{r}
preds_autonomic <- compare_predictors("Disorders_Somatic_AutonomicDysfunction")
display_models(preds_autonomic$table, title="Best Predictor", subtitle = "Autonomic Dysfunction")
preds_autonomic$p
mods_autonomic <- compare_models_glm("Disorders_Somatic_AutonomicDysfunction",
                                     title="Autonomic Dysfunction",
                                     subtitle = "Hypermobility, chest pain, hypo/hypertension, ....")
display_models(mods_autonomic$table, title="Best Model", subtitle = "Autonomic Dysfunction")
mods_autonomic$p
```

@@

```{r}
preds_immune <- compare_predictors("Disorders_Somatic_ImmuneInflammatory")
display_models(preds_immune$table, title="Best Predictor", subtitle = "Immune-Inflammatory Symptoms")
preds_immune$p
mods_immune <- compare_models_glm("Disorders_Somatic_ImmuneInflammatory",
                                  title="Immune-Inflammatory Symptoms",
                                  subtitle = "Allergies, asthma, eczema, autoimmune, ...")
display_models(mods_immune$table, title="Best Model", subtitle = "Immune-Inflammatory Symptoms")
mods_immune$p
```

@@

```{r}
preds_age <- compare_predictors("Age")
display_models(preds_age$table, title="Best Predictor", subtitle = "Age")
preds_age$p
mods_age <- compare_models_lm("Age")
display_models(mods_age, title="Best Model", subtitle = "Age")
```

@@

preds_sex <- compare_predictors("Sex")
display_models(preds_sex$table, title="Best Predictor", subtitle = "Sex")
preds_sex$p
mods_sex <- compare_models_glm("Sex")
display_models(mods_sex$table, title="Best Model", subtitle = "Sex")
mods_sex$p
```

@@

```{r}
preds_bmi <- compare_predictors("BMI")
display_models(preds_bmi$table, title="Best Predictor", subtitle = "BMI")
preds_bmi$p
mods_bmi <- compare_models_lm("BMI")
display_models(mods_bmi, title="Best Model", subtitle = "BMI")
```

@@

```{r}
preds_physactiv <- compare_predictors("Physical_Active")
display_models(preds_physactiv$table, title="Best Predictor", subtitle = "Physical Activity")
preds_physactiv$p
mods_physactiv <- compare_models_lm("Physical_Active")
display_models(mods_physactiv, title="Best Model", subtitle = "Physical Activity")
```

@@

```{r}
preds_wearN <- compare_predictors("Wearables_Number", family = "poisson")
display_models(preds_wearN$table, title="Best Predictor", subtitle = "Wearables Number")
preds_wearN$p
```

@@

```{r}
df$Wearables_HeartOwn <- ifelse(df$Wearables_Heart == "Not owning", 0, 1) 
preds_wearHeartOwn <- compare_predictors("Wearables_HeartOwn")
display_models(preds_wearHeartOwn$table, title="Best Predictor", subtitle = "Wearables Heart Ownership")
preds_wearHeartOwn$p
mods_wearHeartOwn <- compare_models_glm("Wearables_HeartOwn")
display_models(mods_wearHeartOwn$table, title="Best Model", subtitle = "Wearables Heart Ownership")
mods_wearHeartOwn$p

preds_wearHeartImp <- compare_predictors("Wearables_HeartImportance")
display_models(preds_wearHeartImp$table, title="Best Predictor", subtitle = "Wearables Heart Importance")
preds_wearHeartImp$p
mods_wearHeartImp <- compare_models_lm("Wearables_HeartImportance")
display_models(mods_wearHeartImp, title="Best Model", subtitle = "Wearables Heart Importance")
```

@@

```{r}
df$Wearables_SleepOwn <- ifelse(df$Wearables_Sleep == "Not owning", 0, 1)
preds_wearSleepOwn <- compare_predictors("Wearables_SleepOwn")
display_models(preds_wearSleepOwn$table, title="Best Predictor", subtitle = "Wearables Sleep Ownership")
preds_wearSleepOwn$p
mods_wearSleepOwn <- compare_models_glm("Wearables_SleepOwn")
display_models(mods_wearSleepOwn$table, title="Best Model", subtitle = "Wearables Sleep Ownership")

preds_wearSleepImp <- compare_predictors("Wearables_SleepImportance")
display_models(preds_wearSleepImp$table, title="Best Predictor", subtitle = "Wearables Sleep Importance")
preds_wearSleepImp$p
mods_wearSleepImp <- compare_models_lm("Wearables_SleepImportance")
display_models(mods_wearSleepImp, title="Best Model", subtitle = "Wearables Sleep Importance")
```
